The Place of the Local Group in the Cosmic Web

### 2014-05-23 paper/main.tex
corrected p value abstract
new plots
writing again

@@

\title{The Place of the Local Group in the Cosmic Web} 
\author{
  XXXX\altaffilmark{1},
  YYYY\altaffilmark{2},
  ZZZZ\altaffilmark{3}
}

\altaffiltext{1}{Uni A}
\altaffiltext{2}{Uni B}
\altaffiltext{3}{Uni C}
\begin{abstract}
In this Letter we explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$ CDM cosmology.
We use a description for the cosmic web that uses the Hessian of the
gravitational potential to classify a nieghborhodd in the simulation
as either peak, sheet, filament or voids. We find that the LG pairs
are preferentially located in filaments and sheets. Locally their
locations are also located in a narrow range of overdensity
$0<\delta<4$, ellipticity $0.2<e<1.0$ and prolateness
$-0.5<p<0.5$. Furthermore we find a strong anti-alignment between the
LG angular momentum vector and the filament lines and the sheet 
planes.  
\end{abstract}

@@

%larger scales & lg env
To understand better the properties of the LG and how this uncommon
pair configuration fit in the cosmological context, an immediate
question arise. What else can we say of the LG at larger scales?. In
particular, which are the typical/prefered locations of these systems
within the Cosmic Web?.

Looking the LG at larger scales we have it is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, $M101$, $M81$, $NGC1023$, Cen A
group. At this scale, there is no evident alignment of the MW-M31
orbital plane with the local filament or the Virgo-Fornax direction.

However, if we look in a smaller volume below scales of $\sim 6$ \mpc,
there is a clear alignment of th the MW-M31 orbit with a local plane
as shown by figure $3$ in \citet{2013AJ....146...69C}.

%this paper.
In this paper we will study the large scale environment of LG
analogues using the Bolshoi simulation, in particular which kind of
structures they reside and if there is any correlation or alignment
with the cosmic web.   Environment is defined by the cosmic web
components identified by \citet{Tweb}, and we use the LG analogues
computed by \citet{lganalogues}.

@@

\begin{equation}
T_{ij} = \frac{\partial^2 \phi}{\partial r_i \partial r_j}, 
\end{equation}
%
where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
coordiates and $\phi$ is the gravitational potential renormalized to
follow the following Poisson equation $\nabla\phi=\delta$ where
$\delta$ is the matter overdensity.

This tensor is real and symmetric, which means that can be
diagonalized. We note the eigenvalues as $\lambda_1\geq \lambda_2\geq
\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
$\hat{e}_2$ and $\hat{e}_3$. The web classification compares each one
of the three eigenvalues to a threshold value $\lambda_{\rm th}$. If
the three, two, one or zero eigenvalues are larger than this threshold
the region es classified as peak, filament, sheet or void,
respectively.

In \cite{Tweb} we perform a detailed study for the topology of the
cosmic web and its visual counterpart as a function of the parameter
$\lambda_{\rm th}$. We find that reasonable results in terms of the
volume fraction occupied by voids, the visual inspection and the halo
populations in each web type can be reached by values of $0.2<\lambda_{\rm
th}<0.4$. In this paper we choose the value of $\lambda_{\rm
  th}=0.3$. We have veryfied that the main trends reported in this
paper are unsensitive to the choice of that parameter, as long as it
is in the range already quoted.

The algorithm to compute the potential is grid based. First we
interpolate the density into a cubic grid and smooth it with a
gaussian kernel. Then we obtain the gravitational potential and use
finite differences to compute the Hessian at every point in the
grid. Physically speaking, the cosmic web features are scale
dependent and the grid size has to be chosen with respect to the
physical scales of the problem at hand.

In our case we have used a grid size on and a gaussian smoothing with
two times larger as the typical separation between the two
halos in the Local Group. The objective is to have both halos in the
pair a common environment. In this paper we use a grid spacing of
$s=1.024$ \hMpc, corresponding to a $256^3$ grid in the Bolshoi
volume. The scale for the gaussian smoothing uses the same value.

We use the matter overdensity, ellipticity and the prolatenes to characterize
the relative strength of the three eigenvalues. These quantities are
defined in terms of the eigenvalues as follows

\begin{equation}
\delta = \lambda_1 + \lambda_2 + \lambda_3,
\end{equation}

\begin{equation}
e= \frac{\lambda_3 - \lambda_1}{2(\lambda_1 + \lambda_2 + \lambda_3)}, 
\end{equation}
%
\begin{equation}
p= \frac{\lambda_1 + \lambda_3 - 2\lambda_2}{2(\lambda_1 + \lambda_2 +
  \lambda_3)}.
\end{equation}

@@

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{ELL_histogram.pdf}
  \includegraphics[width=0.49\textwidth]{PROL_histogram.pdf}
\end{center}
\caption{Cumulative distributions for the ellipticity and prolateness.
    \label{fig:ELL_PROL}}  
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
3$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{alignments_e3.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector $\hat{n}$ and the third eigenvector $\vec{e}_3$.
    \label{fig:alignment}}  
\end{figure}

%\begin{table}
%\begin{center}
%\begin{tabular}{lccc}\hline\hline
%Sample & $\langle\hat{e}_1\cdot \hat{n}\rangle$ & $\langle\hat{e}_2\cdot \hat{n%}\rangle$ & $\langle\hat{e}_3\cdot \hat{n}\rangle$\\\hline
%2$\sigma$ & 0.56 & 0.53 &  0.33\\
%3$\sigma$ & 0.51 & 0.51 &  0.46\\
%General & 0.54 & 0.52 & 0.40\\\hline
%\end{tabular}
%\caption{Average values for the cosinus between the three eigenvectors and the %vector normal to the orbital plane.
%\label{table:mu}}
%\end{center}
%\end{table}

>>>>

\shorttitle{The Local Group in the Cosmic Web}
\shortauthors{Forero-Romero \& Gonz\'alez}

@@

\title{The Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$, and R. Gonz\'alez$^2$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrofísica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
}
\email{je.forero@uniandes.edu.co}

\begin{abstract}
In this Letter we explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$ CDM cosmology.
We use a description for the cosmic web that uses the Hessian of the
gravitational potential to classify a nieghborhodd in the simulation
as either peak, sheet, filament or voids. We find that the LG pairs
are preferentially located in filaments and sheets. Locally their
locations are also located in a narrow range of overdensity
$0<\delta<4$, ellipticity $0.1<e<1.0$ and prolateness
$-0.5<p<0.5$. Furthermore we find a strong anti-alignment between the
LG angular momentum vector and the filament lines and the sheet 
planes.  
\end{abstract}

@@

%larger scales & lg env
To better understand the properties of the LG and how this uncommon
pair configuration fit in the cosmological context, an immediate
question arise. What else can we say of the LG at larger scales?. In
particular, which are the typical/prefered locations of these systems
within the Cosmic Web?.

Looking the LG at larger scales we have it is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, $M101$, $M81$, $NGC1023$, Cen A
group. At this scale, there is no evident alignment of the MW-M31
orbital plane with the local filament or the Virgo-Fornax
direction. However, if we look in a smaller volume below scales of
$\sim 6$ \mpc, there is a clear alignment of th the MW-M31 orbit with
a local plane as shown by figure $3$ in \citet{2013AJ....146...69C}.

%this paper.
In this Letter we study the large scale environment of LG 
analogues in the context of $\Lambda$CDM. We use the Bolshoi
simulation to explore in what structures they reside and if there is
any correlation or alignment with the cosmic web. The large scale
Environment is defined by the cosmic web components identified by
\citet{Tweb}, and we use the LG analogues computed by
\citet{lganalogues}.

@@

\begin{equation}
T_{ij} = \frac{\partial^2 \phi}{\partial r_i \partial r_j}, 
\end{equation}
%
where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
coordiates and $\phi$ is the gravitational potential renormalized to
follow the following Poisson equation $\nabla^2\phi=\delta$ where
$\delta$ is the matter overdensity.

This tensor is real and symmetric, which means that can be
diagonalized. We note its eigenvalues as $\lambda_1\geq \lambda_2\geq
\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
$\hat{e}_2$ and $\hat{e}_3$. The web classification compares each one
of the three eigenvalues to a threshold value $\lambda_{\rm th}$. If
the three, two, one or zero eigenvalues are larger than this threshold
the region is classified as peak, filament, sheet or void,
respectively.

\cite{Tweb} performed a detailed study for the topology of the
cosmic web and its visual counterpart as a function of the parameter
$\lambda_{\rm th}$. They found that reasonable results in terms of the
volume fraction occupied by voids, the visual inspection and the halo
populations in each web type can be reached by values of $0.2<\lambda_{\rm
th}<0.4$. In this Letter we choose the value of $\lambda_{\rm
  th}=0.3$ to proceed with our analysis. We have veryfied that the
main trends reported in this paper are unsensitive to the choice of
that parameter, as long as it is in the range already quoted.

The algorithm to compute the potential is grid based. First we
interpolate the density into a cubic grid with a Cloud-In-Cell (CIC)
scheme and smooth it with a gaussian kernel. Then we obtain the
gravitational potential using FFT methods and use finite differences
to compute the Hessian at every point in the grid. In our case we have
used a grid size on and a gaussian smoothing with two times larger as
the typical separation between the two halos in the Local Group. The
purpose of this choice is to have both halos in the pair a common
environment. In this paper we use a grid spacing of $s=1.024$ \hMpc,
corresponding to a $256^3$ grid in the Bolshoi volume. The scale for
the gaussian smoothing uses the same value.

After computing the eigenvalues and eigenvectors on each point of the
grid we use the matter overdensity, ellipticity and the prolatenes to
further characterize the web. These quantities are defined in terms of the
eigenvalues as follows 
%
\begin{equation}
\delta = \lambda_1 + \lambda_2 + \lambda_3,
\end{equation}
%
\begin{equation}
e= \frac{\lambda_3 - \lambda_1}{2(\lambda_1 + \lambda_2 + \lambda_3)}, 
\end{equation}
%
\begin{equation}
p= \frac{\lambda_1 + \lambda_3 - 2\lambda_2}{2(\lambda_1 + \lambda_2 +
  \lambda_3)}.
\end{equation}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e3_filament.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_sheet.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector $\hat{n}$ and the third eigenvector $\vec{e}_3$.
    \label{fig:alignment}}  
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{ELL_histogram_filament.pdf}
  \includegraphics[width=0.49\textwidth]{PROL_histogram_filament.pdf}
  \includegraphics[width=0.49\textwidth]{ELL_histogram_sheet.pdf}
  \includegraphics[width=0.49\textwidth]{PROL_histogram_sheet.pdf}
\end{center}
\caption{Cumulative distributions for the ellipticity and prolateness.
    \label{fig:ELL_PROL}}  
\end{figure*}

@@

@@

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table}

@@
